Calendar-based graphics for visualising people's daily schedules

### 2017-07-16 main.Rmd
minor tweaks about references
expanding some figure captions

```{r flinders-polar, fig.height = 6.5, fig.cap = "Line glyphs on polar coordinates."}
```

@@

The comparison of one sensor to another adds additional insights to the dataset, which is commonly done with an overlaying plot such as Figure \ref{fig:overlay}. For instance, the dominant patterns occurred to both train stations--Flinders Street Station and Flagstaff station--are together driven by the commuters on the work days; however, the former is overwhelmed by the number of pedestrians during the weekends and public holidays, compared to the latter. It suggests that Flagstaff station limits its functionality as simply the public transport hub for day-to-day commuters, but various activities take place around the Flinders Street Station other than commuting. Because Flinders Street Station closely lies to South Bank and other places of attractions where the locals go for leisure and the tourists for travelling. It can be noted from Figure \ref{fig:overlay} that State Library follows the similar temporal trend as Flinders Street Station on non-work days. The nighttime events, such as White Night and New Year Evening Firework, has barely affected the operation of Flagstaff Station but heavily affected the incoming and outgoing traffic to Flinders Street Station and State Library on these days.

@@

```{r facet, fig.height = 11, fig.cap = "Line graphs faceted by the 3 sensors in the 6 by 2 monthly calendar."}
```

@@

```{r write-bib}
write_bib(c(.packages(), "geofacet"), 'packages.bib')
```

>>>>

```{r flinders-polar, fig.height = 6.5, fig.cap = "Star plots of hourly pedestrian counts at Flinders Street Station, which are line charts placed in polar coordinates. The periodic behaviours on workdays are clearly visible."}
```

@@

The comparison of one sensor to another adds additional insights to the dataset, which is commonly done with an overlaying plot such as Figure \ref{fig:overlay}. For instance, the dominant patterns occurred to both train stations--Flinders Street Station and Flagstaff station--are together driven by the commuters on the work days; however, the former is much outnumbered than the latter during the weekends and public holidays. It suggests that Flagstaff station limits its functionality as simply the public transport hub for day-to-day commuters, but various activities take place around the Flinders Street Station other than commuting. Because Flinders Street Station closely lies to South Bank and other places of attractions where the locals go for leisure and the tourists for travelling. It can be noted from Figure \ref{fig:overlay} that State Library follows the similar temporal trend as Flinders Street Station on non-work days. The nighttime events, such as White Night and New Year Evening Firework, has barely affected the operation of Flagstaff Station but heavily affected the incoming and outgoing traffic to Flinders Street Station and State Library on these days.

@@

```{r facet, fig.height = 11, fig.cap = "Line charts, embedded in the 6 by 2 monthly calendar, coloured and faceted by the 3 sensors. The variations of an individual sensor are emphasised, and the shapes can be compared across the cells and sensors."}
```

@@

```{r write-bib}
write_bib(.packages(), 'packages.bib')
```

### 2017-07-16 main.tex
expanding some figure captions

\caption[Line glyphs on polar coordinates]{Line glyphs on polar coordinates.}\label{fig:flinders-polar}
\end{figure}
\end{CodeChunk}

@@

\caption[Line graphs faceted by the 3 sensors in the 6 by 2 monthly calendar]{Line graphs faceted by the 3 sensors in the 6 by 2 monthly calendar.}\label{fig:facet}
\end{figure}
\end{CodeChunk}

>>>>

\caption[Star plots of hourly pedestrian counts at Flinders Street Station, which are line charts placed in polar coordinates]{Star plots of hourly pedestrian counts at Flinders Street Station, which are line charts placed in polar coordinates. The periodic behaviours on workdays are clearly visible.}\label{fig:flinders-polar}
\end{figure}
\end{CodeChunk}

@@

\caption[Line charts, embedded in the 6 by 2 monthly calendar, coloured and faceted by the 3 sensors]{Line charts, embedded in the 6 by 2 monthly calendar, coloured and faceted by the 3 sensors. The variations of an individual sensor are emphasised, and the shapes can be compared across the cells and sensors.}\label{fig:facet}
\end{figure}
\end{CodeChunk}
